### 2014-10-29 motivation.tex

\noindent It takes a list of effects (the \emph{context} for the operation), an
argument and returns a result along with an optional effect. Read-only
operations do not return any effect. If an effect is returned, it is added to
the state of the object at the current replica, and asynchronously sent to
other replicas. The implementation of the bank account operations in \name is
given below:

@@

getBalance :: [Acc] -> () -> (Int, Maybe Acc)
getBalance ctxt _ =
  let res = sum [x | Deposit_ x <- ctxt]
						- sum [x | Withdraw_ x <- ctxt]
	in (res, Nothing)

>>>>

\noindent An operation takes a list of effects (the \emph{context} for the operation), an
argument and returns a result along with an optional effect. Read-only
operations do not return any effect. If an effect is returned, it is added to
the state of the object at the current replica, and asynchronously sent to
other replicas. The implementation of the bank account operations in \name is
given below:

@@

getBalance :: [Acc] -> () -> (Int, Maybe Acc)
getBalance ctxt _ =
  let res = sum [x | Deposit x <- ctxt]
          - sum [x | Withdraw x <- ctxt]
	in (res, Nothing)
